---
title: "Spotify-Remoji Vignette"
author: "Daniel Raff, Alexander Kleefeldt, Siobhan McCarter and Charley Carriero"
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_document: default
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

## Overview

**spotifyremoji** is a package designed for working with the Spotify API. <br/>

<br/>

Our package provides an easy and guided experience for working with your Spotify data. As Spotify imposes restrictions on 
who can access their API, only Spoitfy members/users will be able to get the authentication-token requried to make use
of this package. Instructions for how to generate an authentication-token can be found in the ReadMe document. 

<br/>

The following functions are included:

* `artist_popularity()`: Compares the popularity and genre of three artists via a bar plot visualization. 
* `related_artists()`:   Identifies related artists to a given input artist. Returns a dataframe containing artist names. 
* `get_top_artists_for_user()`: Finds a users top artists over an input time range. Returns a dataframe containing summary information on each artist. 

<br/>

## Installation

Install this package directly from GitHub:

```{r install,  message=FALSE}
devtools::install_github("akleefel/spotifyremoji")
```

<br/>

## Usage

```{r usage, message = FALSE}
# load the package 
library(spotifyremoji)

# Obtain an authentication token by following the instructions in the README

# compare artists (output ggplot)
artist_popularity(my_token, 'vybz kartel', 'candlemass', 'brockhampton')


# get related artists  (output dataframe)
related_artists(my_token, 'Haftbefel')


# get your top artists (output dataframe)
get_top_artists_for_user(my_token, 50, 2)
```



